Temporal graph realization from fastest paths

### 2024-01-11 SAND2024/SAND24-longversion.tex
changes 10th jan - small changes to full version Nina

    Having computed $G$, our algorithm proceeds as follows. We pick an arbitrary edge $f$ and give it label one, that is, $\lambda(f)=1$. Now we push all edges incident with $f$ into a (initially empty) queue. Now we repeat the following as long as the queue is not empty:
\begin{itemize}
    \item Pop edge $e=\{u,v\}$ from the queue. Since $e$ was pushed into the queue, there is an edge $e'$ incident with $e$ that already obtained a label. Let w.l.o.g.\ $e'=\{v,w\}$. Then we set $\lambda(e)=(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
    \item Push all edges incident with $e$ that have not received a label yet into the queue.
\end{itemize}
When the queue is empty, all edges have received a label. Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$. If this check succeeds for all vertex pairs, output the labelling $\lambda$, otherwise abort.

@@

	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$,

@@

	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$, and let us

@@

    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a line segment in $G'$.

@@

\begin{observation}\label{obs:FirstLabelAndDuration}
    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
    Symmetrically, knowing $\lambda(e_p)$ and $d(P)$, we can uniquely determine $\lambda(e_1)$.
\end{observation}
The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}. This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
where the label of last edge is considered with some delta periods,
\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.

@@

Now to label $P$ we use the fact that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$, 
therefore we can label each edge using \cref{obs:FirstLabelAndDuration},
where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$ and 
we set the label of the first edge of $P$ to be a constant $c\in [\Delta]$.
This gives us a unique label for each edge of $P$, that depends on the value $\lambda(u v_2)$.
\end{proof}

@@

\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
Let $S_{u,v}$ be a segment in $G$ of length at least $5$,
\ie $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
It cannot happen that an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$,
is not a part of any fastest temporal path, of length at least $2$, between vertices in $S_{u,v}$,
\ie there has to be a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through edge $f$.
In the case when $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it.
\end{lemma}

@@

    \emph{Case 1: }$f = v_2v_3$.
    Let us observe the case of fastest temporal paths between $v_{1}$ and $v_{3}$.
    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
    From our proposition it follows that
    \begin{itemize}
        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
    is of the following form 
    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
    and
        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
    is of the following form 
    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
    \end{itemize}
    It follows that 
    $
    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
    $
    and
    $
    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
    $.
    Let 
    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
    Summing now both of the above equations we get
    \begin{equation}
    \begin{split} \label{eq:FPT-prf-fUnlabeled}
        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
        %
        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
        %
        3 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
        &\leq 
        1 + (t_2 - t_1)_\Delta + 
        1 + (t_1 - t_2)_\Delta\\
        %
        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
        &\leq 
        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
    \end{split}
    \end{equation}
    Note that if $t_i \neq t_j$ we get that 
    the sum
    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
    and if $t_i = t_j$ the sum equals $2\Delta$.
    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
    for any relation of labels $t_1,t_2, \dots, t_5$,
    which is a contradiction.

@@

    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, between vertices in $S{_u,v}$, avoid an edge $f$.

    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
    Suppose that the fastest temporal paths between $v_1$ and $v_3$ do not use the edge $f$.
    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
    which is of the form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
    and similarly 
    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
    of the form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
    Again we get the following.
    \begin{equation*}
    \begin{split}
        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
        %
        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
        %
        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
        &\leq 
        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
    \end{split}
    \end{equation*}
    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
    since in this case the left hands side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.

    Repeating the analysis for the fastest paths between $v_2$ and $v_4$,
    we get that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
    Altogether, we get that $f$ is not in a fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
\end{proof}

\subsubsection{Adding constraints and variables to the ILP}\label{sec:constraints}
We start by analyzing the case where we want to determine the labels on fastest temporal paths between vertices of interest.
We proceed in the following way.
Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
We call these $\ell - 1$ edges, \emph{partially determined} edges.
After repeating this step for all pairs of vertices in $U$,
the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
or are partially determined.
If the fastest temporal path between two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
are called the \emph{not yet determined} edges.
Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path.

@@

We will now relate also these edges.

@@

    Thus we create $4$ guesses for every such segment $S_{u,v}$, therefore we create $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.

@@

In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$. But in this case we get that $3$ labels of edges in the segment have to be the same, while one is different,
which results in a segment with two not yet determined edges.

@@

From now on we refer to segments of length less than $4$.

At this point $G$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
or it depends on no other label.
We now describe how we create variables and start building our ILP instances. 
For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
Besides that we create one variable for each edge that is still not yet determined on a segment.
Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
At the end we create our final guess.
\begin{enumerate}[G-1.]
% counter for guesses continues
\setcounter{enumi}{\value{guesscounter}}
%%
    \item \label{FPT:guessallPermutations}
We guess the permutation of all $O(k^2)$ variables,
together with the relation of each variable to the labels of edges incident to these not yet determined edges.
Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
which are determined by some other label,
and variables of the not yet determined neighbors,
and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
This results in $O(k^2)! = k^{O(k^2)}$ guesses
and consequently
each of the ILP instances we created up to now is further split into $k^{O(k^2)}$ new ones.
\end{enumerate}
We have now finished creating all ILP instances.
From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
We proceed with adding constraints to each of our ILP instances.
First we add all constraints for the labels of edges that we have determined up to now.
We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths between them.

>>>>

    Having computed $G$, our algorithm proceeds as follows. We pick an arbitrary edge $f$ and give it label one, that is, $\lambda(f)=1$. Now we push all edges incident with $f$ into a (initially empty) queue. Now we repeat the following as long as the queue is not empty:
\begin{itemize}
    \item Pop edge $e=\{u,v\}$ from the queue. Since $e$ was pushed into the queue, there is an edge $e'$ incident with $e$ that already obtained a label. Let w.l.o.g.\ $e'=\{v,w\}$. Then we set $\lambda(e)=(\lambda(e')-D_{u,w}+1)\bmod \Delta$.
    \item Push all edges incident with $e$ that have not received a label yet into the queue.
\end{itemize}
When the queue is empty, all edges have received a label. Iterate over all vertex pairs $u,v$ and check whether the fastest path from $u$ to $v$ in $(G,\lambda)$ has duration $D_{u,v}$. If this check succeeds for all vertex pairs, output the labeling $\lambda$, otherwise abort.

@@

	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$,

@@

	Let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$, and let us

@@

    and let $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$ be a segment in $G'$.

@@

\begin{observation}\label{obs:FirstLabelAndDuration}
    Let $P$ be the underlying path of a fastest temporal path from $u$ to $v$, where $e_1, e_p \in P$ are its first and last edge, respectively.
    Then, knowing the label $\lambda (e_1)$ of the first edge and the duration $d(P,\lambda)$ of the temporal path $(P,\lambda)$, we can uniquely determine the label $\lambda (e_p)$ of the last edge of $P$.
    Symmetrically, knowing $\lambda(e_p)$ and $d(P,\lambda)$, we can uniquely determine $\lambda(e_1)$.
\end{observation}
The correctness of the above statement follows directly from \cref{def:temporalPath+Duration}. This is because the duration of $(P,\lambda)$ is calculated as the difference of labels of last and first edge plus $1$,
where the label of last edge is considered with some delta periods,
\ie $d(P,\lambda) = p_i \Delta + \lambda(e_p) - \lambda (e_1) + 1$, for some $p_i \geq 0$.
Therefore $d(P,\lambda) \pmod \Delta \equiv  (\lambda(e_p) - \lambda (e_1) + 1) \pmod \Delta$.
Note that if $\lambda(e_1)$ and $\lambda(e_p)$ are both unknown, then we can determine one with respect to the other.

@@

Now, to determine the labeling $\lambda$ of the path $P$ we use the property that the fastest temporal path from $u$ to any $v_i \in P$ is a subpath of $P$. 
We set the label of the first edge of $P$ to be a constant $c\in [\Delta]$
and
use \cref{obs:FirstLabelAndDuration} to label all remaining edges,
where the duration from $u$ to $v_i$ equals to $D_{u,v_i}$.
This gives us a unique labeling $\lambda$ of $P$ where the label of each edge of $P$ is a function of $c$.
\end{proof}

@@

\begin{lemma}\label{lemma:FPT-noUndeterminedEdgeInSegment}
Let $S_{u,v}$ be a segment in $G$ of length at least $5$, denoted as $S_{u,v}= (u=v_1,v_2, \dots, v_p = v)$, where $p > 5$.
It is impossible for an inner edge $f = v_i v_{i+1}$ from $S_{u,v} \setminus \{u,v\}$ (where $f$ is an edge that is not incident to a vertex from $U$)
to not be a part of any fastest temporal path, of length at least $2$ between vertices in $S_{u,v}$.
In other words, there must exist a pair $v_j, v_{j'} \in S_{u,v}$ \st the fastest temporal path from $v_j$ to $v_{j'}$ passes through $f$.
In the case where $p = 5$ all temporal paths of length $2$ avoid $f$ if and only if $f$ has the same label as both of the edges incident to it, while the label of the last remaining edge is a function of $\lambda(f)$.
\end{lemma}

@@

    \emph{Case 1: }$f = v_2v_3$.
    Let us observe the case of fastest temporal paths between $v_{1}$ and $v_{3}$.
    Denote with $Q = (v_{1}, v_2, v_3)$ and with $P' = (v_3,v_4,v_5,v_6)$.
    From our proposition it follows that
    \begin{itemize}
        \item the fastest temporal path $P ^ +$ from $v_1$ to $v_3$ 
    is of the following form 
    $P^+ = v_{1}  \leadsto v_6 \rightarrow v_5 \rightarrow v_4 \rightarrow v_3$,
    and
        \item the fastest temporal path $P ^ -$ from $v_{3}$ to $v_{1}$ 
    is of the following form 
    $P^- = v_{3} \rightarrow v_{4} \rightarrow v_5 \rightarrow v_6 \leadsto v_1$.
    \end{itemize}
    It follows that 
    $
    d(v_{1}, v_{3}, P^+) \leq d(v_{1}, v_{3}, Q),
    $
    and
    $
    d(v_{1}, v_{3}, P^-) \leq d(v_{1}, v_{3}, Q)
    $. 
    Note that $d(v_{1}, v_{3}, P^+) \geq 1 + d(v_6,v_3,P')$,
    and by the definition $d(v_6,v_3,P') = 1 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta$,
    where $(t_i - t_j)_\Delta$ denotes the difference of two consecutive labels $t_i, t_j$ modulo $\Delta$.
    Similarly holds for $d(v_{1}, v_{3}, P^+)$.
    Summing now both of the above equations we get
    \begin{equation}
    \begin{split} \label{eq:FPT-prf-fUnlabeled}
        d(v_{1}, v_{3}, P^+) + d(v_{3}, v_{1}, P^-) &\leq 
        d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
        %
        1 + d(v_6,v_3,P') + 1 + d(v_3,v_6,P') &\leq d(v_{1}, v_{3}, Q) + d(v_{3}, v_{1}, Q) \\
        %
        3 + (t_4 - t_5)_\Delta + (t_3 - t_4)_\Delta +
        1 + (t_4 - t_3)_\Delta + (t_5 - t_4)_\Delta 
        &\leq 
        1 + (t_2 - t_1)_\Delta + 
        1 + (t_1 - t_2)_\Delta\\
        %
        (t_4 - t_5)_\Delta + (t_5 - t_4)_\Delta +
        (t_4 - t_3)_\Delta + (t_3 - t_4)_\Delta  + 2 
        &\leq 
        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.
    \end{split}
    \end{equation}
    Note that if $t_i \neq t_j$ we get that 
    the sum
    $(t_i - t_j)_\Delta + (t_j - t_i)_\Delta$ equals exactly $\Delta$,
    and if $t_i = t_j$ the sum equals $2\Delta$.
    This follows from the definition of travel delays at vertices (see \cref{obs:travel-delays-both-directions}).
    Therefore we get from \cref{eq:FPT-prf-fUnlabeled}, 
    that the right part is at most $2 \Delta$, while the left part is at least $2 \Delta + 1$,
    for any relation of labels $t_1,t_2, \dots, t_5$,
    which is a contradiction.

@@

    In the case when $S_{u,v}$ is longer, we would get even bigger number on the left hand side of \cref{eq:FPT-prf-fUnlabeled}, 
    so we conclude that in all of the above cases, it cannot happen that all fastest paths of length $2$, between vertices in $S_{u,v}$, avoid edge $f$.

    Let us observe now the case when $S_{u,v} = (u=v_1,v_2, v_3, v_4, v_5=v)$ is of length $4$.
    Let $f = v_2 v_3$ (the case with $f = v_3 v_4$ is symmetrical).
    Suppose that the fastest temporal paths between $v_1$ and $v_3$ do not use the edge $f$.
    We denote with $R^+$ the fastest path from $v_1$ to $v_3$, 
    which is of the form $u \leadsto v \rightarrow v_4 \rightarrow v_3$,
    and similarly 
    with $R^-$ the fastest path from $v_3$ to $v_1$, which is
    of the form $v_3 \rightarrow v_4 \rightarrow v \leadsto u$.
    We denote with $R' = (v_3, v_4, v_5)$ and with $S = (v_1,v_2,v_3)$.
    Again we get the following.
    \begin{equation*}
    \begin{split}
        d(v_{1}, v_{3}, R^+) + d(v_{3}, v_{1}, R^-) &\leq 
        d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
        %
        1 + d(v_5,v_3,R') + 1 + d(v_3,v_5,R') &\leq d(v_{1}, v_{3}, S) + d(v_{3}, v_{1}, S) \\
        %
        (t_3 - t_4)_\Delta + (t_4 - t_3)_\Delta + 2 
        &\leq 
        (t_2 - t_1)_\Delta + (t_1 - t_2)_\Delta.        
    \end{split}
    \end{equation*}
    The only case when the equation has a valid solution is when $t_1 = t_2$ and $t_3 \neq t_4$,
    as in this case the left hand side evaluates to $\Delta + 2$, while the right side evaluates to $2 \Delta$.
    %
    Repeating the analysis for the fastest paths between $v_2$ and $v_4$,
    we conclude that the only valid solution is when $t_2 = t_3$ and $t_1 \neq t_4$.
    %
    Altogether, we get that $f$ is not a part of any fastest path of length $2$ in $S_{u,v}$ if and only if the label of edge $f$ is the same as the labels on the edges incident to it, while the last remaining edge has a different label.
    %
    Note now that the fastest temporal path from $v_2$ to $v_4$ must first use the edge $u v_2$ and finish with the edge $v_4 v_5$, and it has to be of duration $D_{v_2, v_4}$. Using \cref{lemma:FPT-uv-Labelalledges} we determine the label of the edge $v_4v_5$ as a function of $\lambda(f)$.
\end{proof}

\subsubsection{Adding constraints and variables to the ILP}\label{sec:constraints}
We start by analyzing the case where we want to determine the labels on fastest temporal paths between vertices of interest.
We proceed in the following way.
Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
If $P_{u,v}$ is a segment we determine all the labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-Labelalledges}).
%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
In the case when $P_{u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P_{u,v}$, with respect to the label of the first edge (see \cref{lemma:FPT-uv-LabelAlmostalledges}).
We call these $\ell - 1$ edges, \emph{partially determined} edges.
After repeating this step for all pairs of vertices in $U$,
the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path,
or are partially determined.
If the fastest temporal path between two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
All other edges in $G'$ %that were not determined with the respect to some other edge label up to now, or are not partially determined, 
are called the \emph{not yet determined} edges.
Note that the not yet determined edges are exactly the ones that are not a part of any fastest temporal path between any two vertices in $U$.

@@

We now relate also some of these edges.

@@

    Thus we create $4$ guesses for every such segment $S_{u,v}$, and $O(k^2)$ new guesses in total, as there are at most $O(k^2)$ segments.

@@

In the case when segment has $4$ edges, it can happen that the fastest temporal paths from above, do not traverse $f$. But in this case we know that three edges have the same label, denote it $c$, while the label of the last one is a function of $c$.

@@

%From now on we refer to segments of length less than $4$.

At this point $G'$ is a graph, where each edge $e$ has a value for its label $\lambda(e)$
that depends on (\ie is a function of) some other label $\lambda(f)$ of edge $f$,
or it depends on no other label.
We now describe how we create variables and start building our ILP instances. 
For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
Besides that we create one variable for each edge that is still not yet determined on a segment.
Since each vertex of interest is incident to at most $k$ edges, and each segment has at most one extra not yet determined edge, we create $O(k^2)$ variables.
At the end we create our final guess.
\begin{enumerate}[G-1.]
% counter for guesses continues
\setcounter{enumi}{\value{guesscounter}}
%%
    \item \label{FPT:guessallPermutations}
We guess the permutation of all $O(k^2)$ variables,
together with the relation of each variable to the labels of edges incident to these not yet determined edges.
Namely, for an edge $e$ that is not yet determined, we set its value to $x_e$ and check labels of all of its neighbors,
which are determined by some other label,
and variables of the not yet determined neighbors,
and guess if $x_e$ is smaller, equal or bigger than the labels of the edges of its neighbors.
So, for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$,
and for any neighboring edge $g$ of $e$ we know if $x_e < \lambda(g)$ or 
$x_e = \lambda(g)$, or $x_e > \lambda(g)$.
This results in $O(k^2)! = k^{O(k^2)}$ guesses
and consequently
each of the ILP instances we created up to now is further split into $k^{O(k^2)}$ new ones.
\end{enumerate}
We have now finished creating all ILP instances.
From \cref{sec:FPT-guessing} we know the structure of all guessed paths, to which we have just added also the knowledge of permutation of all variables.
We proceed with adding constraints to each of our ILP instances.
First we add all constraints for the labels of edges that we have determined up to now.
We then continue to iterate through all pairs of vertices and start adding equality (resp.~inequality) constraints for the fastest (resp.~not necessarily fastest) temporal paths between them.
